---
title: "Football Stats"
author: "Kat Leigh"
date: "2/24/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyr)
library(tidyverse)

```

Let's use the function "kat_football_stats" to calculate catch percentage and catches per minute. First, we need to create some data...

```{r}
data1 <- rnorm(5, 40, 4)
data2 <- 70 + rexp(5, .125)
data3 <- rnorm(5, 40, 10)

```

Now let's plug that data into the function

```{r}
kat_football_stats = function(throws, catches, minutes, wind_speed = 0.03, wind_direction = -0.05, light = 0.05)
  {
  throws = ifelse((throws < 0), return("throws must be greater than zero"), throws)
  catches = ifelse((catches <0), return("catches must be greter than or equal to zero"), catches)
  minutes = ifelse((minutes <0), return("minutes must be greater than zero"), minutes)
  wind_speed = ifelse((wind_speed >1), return("speed must be less than one"), wind_speed)
  wind_direction = ifelse((abs(wind_direction) >1), return("absolute value of direction must be less than one"), wind_direction)
  light = ifelse((!(light %in% c(0.05, 0))), return("light must be a value of 0.05 or zero"), light)
  catch_percentage = ((catches+wind_speed+wind_direction+light)/throws)*100
  catches_per_minute = (catches+wind_speed+wind_direction+light)/minutes
  
  return(c(catch_percentage, catches_per_minute))
}

results <- kat_football_stats(data2,data1,data3)

plot_results <- tibble(outputc = c(results[1:10]), type = c("CP", "CP", "CP", "CP", "CP", "CM", "CM", "CM", "CM", "CM"), minutes = c(data3, data3))
```

Let's plot our results

```{r}
ggplot(plot_results)+
  geom_point(aes(x=minutes, y= outputc, color = type), show.legend = FALSE)+
  labs(title = "Catch Percent and Catches per Minute versus Minutes of Practice for 5 seperate
       hypothetical receiver practice sessions",
       x= "Minutes of Practice Time",
       y= "CM: Catches/Min, CP: % Catches")+
  theme_light()+
  facet_wrap(~type, scales = "free_y")

```

Based on the data entered, more minutes of practice generally result in lower catch rates, but higher catch percentages. The first data point however, bucks this trend. Running this with a larger sample size (greater than 5), would yeild more conclusive results. 